Temperature Effects on Surface Sulfur Dioxide

### 2011-08-24 Cycle-Results.tex
Finished the cycle results sans energies. Now on to introduction, 				 conclusion, and energies!

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/SO-cycle-breakdown-with-cartoons-small.png}
		\caption{}
		\label{fig:cyclic-breakdown}
	\end{center}
\end{figure}
The plot in Figure \ref{fig:cycle-breakdown} shows the distribution of how often the various types of cyclic hydrates were encountered at both cold (blue) and hot (red) temperatures. Each data point shows a percentage of the MD trajectories in which the \suldiox~was a member of a cyclic structure, for different numbers of cyclic waters (up to 4). The two tallest data points, left-most in the plot, show the overall time spent in all types of cyclic structures. Clearly the hot system \suldiox~spends more time in a cyclic structure than at the cold temperature. The plot is based on two criteria for determining if a cyclic structure has formed. (1) The distances between atoms must match the same bonding/distance criteria as used for determining bonding coordinations. (2) The \suldiox~must be minimally in a bonding coordination of type ``SO'', meaning that the sulfur has at least one bonding interaction, and at least one hydrogen-bond must have formed with an oxygen to a neighboring water-hydrogen. As noted earlier in the discussion of the graph-finding routine and the BFS algorithm, the cyclic structures found represent the smallest cycles in which the \suldiox~is a member, based on order of discovery. The \suldiox~will be inevitably involved in other larger and more extended cyclic bonding structures beyond the first one discovered via the BFS. The larger and more extended cyclic structures involving more waters affect the behavior of the hydrogen-bonding network of the water surface. However, we focus here only on the smallest cycles involving the \suldiox~as the most affect the \suldiox~bonding and hydrating behaviors.

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/SO-cycle-breakdown-with-cartoons-small.png}
		\caption{}
		\label{fig:cyclic-breakdown}
	\end{center}
\end{figure}
The plot in Figure \ref{fig:cyclic-breakdown} shows the distribution of how often the various types of cyclic hydrates were encountered at both cold (blue) and hot (red) temperatures. Each data point shows a percentage of the MD trajectories in which the \suldiox~was a member of a cyclic structure, for different numbers of cyclic waters (up to 4). The two tallest data points, left-most in the plot, show the overall time spent in all types of cyclic structures. Clearly the hot system \suldiox~spends more time in a cyclic structure than at the cold temperature. The plot is based on two criteria for determining if a cyclic structure has formed. (1) The distances between atoms must match the same bonding/distance criteria as used for determining bonding coordinations. (2) The \suldiox~must be minimally in a bonding coordination of type ``SO'', meaning that the sulfur has at least one bonding interaction, and at least one hydrogen-bond must have formed with an oxygen to a neighboring water-hydrogen. As noted earlier in the discussion of the graph-finding routine and the BFS algorithm, the cyclic structures found represent the smallest cycles in which the \suldiox~is a member, based on order of discovery. The \suldiox~will be inevitably involved in other larger and more extended cyclic bonding structures beyond the first one discovered via the BFS. The larger and more extended cyclic structures involving more waters affect the behavior of the hydrogen-bonding network of the water surface. However, we focus here only on the smallest cycles involving the \suldiox~as the most affect the \suldiox~bonding and hydrating behaviors.
